Application of computational fluid dynamics and process modelling to investigate low-load operation of a subcritical utility-scale boiler.

### 2022-01-19 ASME_journal/journal-1.1 REVISION/JOURNAL_MANUSCRIPT_BRAD_RAWLINS.tex
Update 2 19/01/2022

\documentclass[review]{elsarticle}
\usepackage[utf8]{inputenc} 
\usepackage{lineno,hyperref}
\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage[fleqn]{amsmath}
\modulolinenumbers[5]

\usepackage{framed}
\usepackage{multicol} % Multiple columns environment

\usepackage{nomencl} % Nomenclature package
\makenomenclature
\setlength{\nomitemsep}{0pt}

\newcommand{\nomunit}[1]{%
  \renewcommand{\nomentryend}{\hspace*{\fill}#1}%
}

\renewcommand\nomgroup[1]{% 
  \item[\bfseries
  \ifstrequal{#1}{A}{Symbols}{%
  \ifstrequal{#1}{B}{Greek symbols}{%
  \ifstrequal{#1}{C}{Abbreviations}{}}}%
]}

\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{\centerline{\thepage}}%
 \let\@evenfoot\@oddfoot}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{frontmatter}

%% Group authors per affiliation:
\author{B.T. Rawlins $^{a}$ \corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{rwlbra001@myuct.ac.za}
\author{R. Laubscher $^b$}
\author{P. Rousseau $^a$}
\address{$^a$ Department of Mechanical Engineering, Applied Thermal-Fluid Process Modelling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
\address{$^b$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}

\begin{abstract}
To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation. Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model. A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers. This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating. The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components. Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation.
\end{abstract}

\begin{keyword}
CFD\sep Boiler \sep Low-load operation \sep Co-simulation
\end{keyword}
\newpage
\end{frontmatter}

\printnomenclature

\nomenclature[A]{$A$}{Area \nomunit{$m^2$}}
\nomenclature[A]{$A_p$}{Particle surface area \nomunit{$m^2$}}
\nomenclature[A]{$A_{pn}$}{Projected particle surface area \nomunit{$m^2$}}
\nomenclature[A]{$A_{c}$}{Carbon pre-exponential factor \nomunit{$s^{-1}$}}
\nomenclature[A]{$A_{vol}$}{Volatile pre-exponential factor \nomunit{$s^{-1}$}}
\nomenclature[A]{$d_p$}{Particle diameter \nomunit{$m$}}
\nomenclature[A]{$E$}{Fluid total energy \nomunit{$J/kg$}}
\nomenclature[A]{$E_{a,c}$}{Carbon activation energy \nomunit{$J/kmol$}}
\nomenclature[A]{$E_{a,vol}$}{Volatile activation energy \nomunit{$J/kmol$}}
\nomenclature[A]{$E_p$}{Particle emission power \nomunit{$W/m^3$}}
\nomenclature[A]{$f_{heat}$}{Near surface char oxidation fraction \nomunit{$-$}}
\nomenclature[A]{$f_{p}$}{Forward scattering factor \nomunit{$-$}}
\nomenclature[A]{$G$}{Incident radiation \nomunit{$W/m^2$}}
\nomenclature[A]{$g$}{Gravitational constant \nomunit{$m/s^2$}}
\nomenclature[A]{$h_{fg}$}{Enthalpy of evaporation \nomunit{$J/kg$}}
\nomenclature[A]{$h_M$}{Mixture enthalpy \nomunit{$J/kg$}}
\nomenclature[A]{$h_{rxn}$}{Enthalpy of reaction \nomunit{$J/kg$}}
\nomenclature[A]{$J_k$ }{Species diffusion flux \nomunit{$m^2/s$}}
\nomenclature[A]{$m_{0,vol}$}{Original mass of volatiles \nomunit{$kg$}}
\nomenclature[A]{$m_{char}$}{Mass of carbon \nomunit{$kg$}}
\nomenclature[A]{$m_{evap}$}{Mass of moisture \nomunit{$kg$}}
\nomenclature[A]{$m_{vol}$}{Mass of volatiles \nomunit{$kg$}}
\nomenclature[A]{$N_{p}$}{Number of particles \nomunit{$-$}}
\nomenclature[A]{$P$}{Perimeter \nomunit{$m$}}
\nomenclature[A]{$p$}{Pressure \nomunit{$Pa$}}
\nomenclature[A]{$p_{O_{2}}$}{Partial pressure of $O_2$ \nomunit{$Pa$}}
\nomenclature[A]{$\dot{Q}_{conv}$}{Convective heat transfer rate \nomunit{$W$}}
\nomenclature[A]{$\dot{Q}_{rad}$}{Radiative heat transfer rate \nomunit{$W$}}
\nomenclature[A]{$\dot{Q}_{w}$}{Wall heat transfer rate \nomunit{$W$}}
\nomenclature[A]{$R$}{Universal gas constant \nomunit{$J/molK$}}
\nomenclature[A]{$R_{c}$}{Carbon reaction rate \nomunit{$s^{-1}$}}
\nomenclature[A]{$R_{diff}$}{Diffusion reaction rate \nomunit{$s^{-1}$}}
\nomenclature[A]{$R_{vol}$}{Volatile reaction rate \nomunit{$s^{-1}$}}
\nomenclature[A]{$T_g$}{Gas temperature \nomunit{$K$}}
\nomenclature[A]{$T_p$}{Particle temperature \nomunit{$K$}}
\nomenclature[A]{$t$}{Time \nomunit{$s$}}
\nomenclature[A]{$u$}{Velocity \nomunit{$m/s$}}
\nomenclature[A]{$V$}{Volume \nomunit{$m^3$}}
\nomenclature[A]{$Y_k$}{Species mass fraction \nomunit{$kg/kg$}}
\nomenclature[A]{$x$}{Quality \nomunit{$-$}}
\nomenclature[B]{$\alpha_g$}{Gas absorption coefficient \nomunit{$m^{-1}$}}
\nomenclature[B]{$\alpha_H$}{Mixture void fraction \nomunit{$-$}}
\nomenclature[B]{$\alpha_p$}{Particle absorption coefficient \nomunit{$m^{-1}$}}
\nomenclature[B]{$\epsilon_p$}{Particle emissivity \nomunit{$-$}}
\nomenclature[B]{$\rho$}{Gas density \nomunit{$kg/m^3$}}
\nomenclature[B]{$\rho_{eff}$}{Effective density \nomunit{$kg/m^3$}}
\nomenclature[B]{$\rho_g$}{Gas density \nomunit{$kg/m^3$}}
\nomenclature[B]{$\rho_l$}{Liquid density \nomunit{$kg/m^3$}}
\nomenclature[B]{$\rho_M$}{Mixture density \nomunit{$kg/m^3$}}
\nomenclature[B]{$\rho_p$}{Particle density \nomunit{$kg/m^3$}}
\nomenclature[B]{$\sigma_{SB}$}{Stefan-Boltzmann constant \nomunit{$W/m^2K^4$}}
\nomenclature[B]{$\sigma_{p}$}{Particle scattering coefficient \nomunit{$m^{-1}$}}
\nomenclature[B]{$\phi$}{Scalar variable \nomunit{$-$}}
\nomenclature[C]{$MCR$}{Maximum continuous rating}
\nomenclature[C]{$CFPP$}{Coal fired power plant}
\nomenclature[C]{$CFD$}{Computational fluid dynamics}
\nomenclature[C]{$SH$}{Superheater}
\nomenclature[C]{$EE$}{Eulerian-Eulerian}
\nomenclature[C]{$WSGGM$}{Weighted sum of gray gas model}
\nomenclature[C]{$RTE$}{Radiative transport equation}
\nomenclature[C]{$HHV$}{Higher heating value}
\nomenclature[C]{$DAF$}{Dry ash free}
\nomenclature[C]{$AR$}{As-received}
\nomenclature[C]{$PA$}{Primary air}
\nomenclature[C]{$SA-AH$}{Secondary air - air heater}
\nomenclature[C]{$SA$}{Secondary air}
\nomenclature[C]{$RH$}{Reheater}
\nomenclature[C]{$ATT$}{Attemperator}
\nomenclature[C]{$EC$}{Economiser}
\nomenclature{\mbox{}}{}
\linenumbers

@@

While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).\\

Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}. The works of Belosevic et al \citep{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40\%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions. The aforementioned research specifically investigated combustion and gas-side effects.\\

Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy. However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\

The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\

@@

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written below in their respective Reynolds.\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}
To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows:
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

@@

A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\

The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \citep{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabular}{lll}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabular}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format journal articles using LaTeX    %
% Written by   Harry H. Cheng, Professor and Director                %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aeronautical Engineering %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use twocolumn and 10pt options with the asme2ej format
\documentclass[twocolumn,10pt]{asme2ej}

\usepackage{graphicx} %% for loading jpg figures
\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color,soul}
\usepackage{xcolor}

\newcommand{\highlight}[1]{%
  \colorbox{yellow!}{$\displaystyle#1$}}
%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

%%% first author
\author{Brad T. Rawlins\thanks{Corresponding author}
    \affiliation{
	Ph.D. Candidate\\
	Department of Mechanical \\Engineering\\
	University of Cape Town\\
    Email: rwlbra001@myuct.ac.za
    \vspace{5mm}
    }

}

%%% second author
%%% remove the following entry for single author papers
%%% add more entries for additional authors
\author{Ryno Laubscher 
    \affiliation{Associate Professor\\
    Department of Mechanical \\Engineering\\
	Stellenbosch University\\
    Email: rlaubscher@sun.ac.za
    }
}

%%% third author
%%% remove the following entry for single author papers
%%% add more entries for additional authors
\author{Pieter Rousseau
    \affiliation{Professor\\
        Department of Mechanical \\Engineering\\
        University of Cape Town\\
        Email: pieter.rousseau@uct.ac.za
    }
}

@@

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation. Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model. A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers. This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating. The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components. Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation.
}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{}{\textit{Variables}}
\entry{$A$}{Area [$m^2$]}
\entry{$A_p$}{Particle surface area [$m^2$]}
\entry{$A_{pn}$}{Projected particle surface area [$m^2$]}
\entry{$A_{c}$}{Carbon pre-exponential factor [$s^{-1}$]}
\entry{$A_{vol}$}{Volatile pre-exponential factor [$s^{-1}$]}
\entry{$d_p$}{Particle diameter [$m$]}
\entry{$E$}{Fluid total energy [$J/kg$]}
\entry{$E_{a,c}$}{Carbon activation energy [$J/kmol$]}
\entry{$E_{a,vol}$}{Volatile activation energy [$J/kmol$]}
\entry{$E_p$}{Particle emission power [$W/m^3$]}
\entry{$f_{heat}$}{Near surface char oxidation fraction [$-$]}
\entry{$f_{p}$}{Forward scattering factor [$-$]}
\entry{$G$}{Incident radiation [$W/m^2$]}
\entry{$g$}{Gravitational constant [$m/s^2$]}
\entry{$h_{fg}$}{Enthalpy of evaporation [$J/kg$]}
\entry{$h_M$}{Mixture enthalpy [$J/kg$]}
\entry{$h_{rxn}$}{Enthalpy of reaction [$J/kg$]}
\entry{$J_k$ }{Species diffusion flux [$m^2/s$]}
\entry{$m_{0,vol}$}{Original mass of volatiles [$kg$]}
\entry{$m_{char}$}{Mass of carbon [$kg$]}
\entry{$m_{evap}$}{Mass of moisture [$kg$]}
\entry{$m_{vol}$}{Mass of volatiles [$kg$]}
\entry{$N_{p}$}{Number of particles [$-$]}
\entry{$P$}{Perimeter [$m$]}
\entry{$p$}{Pressure [$Pa$]}
\entry{$p_{O_{2}}$}{Partial pressure of $O_2$ [$Pa$]}
\entry{$\dot{Q}_{conv}$}{Convective heat transfer rate [$W$]}
\entry{$\dot{Q}_{rad}$}{Radiative heat transfer rate [$W$]}
\entry{$\dot{Q}_{w}$}{Wall heat transfer rate [$W$]}
\entry{$R$}{Universal gas constant [$J/molK$]}
\entry{$R_{c}$}{Carbon reaction rate [$s^{-1}$]}
\entry{$R_{diff}$}{Diffusion reaction rate [$s^{-1}$]}
\entry{$R_{vol}$}{Volatile reaction rate [$s^{-1}$]}
\entry{$S$}{\hl{Mass source term}[$kg/m^3$]}
\entry{$S_m$}{\hl{Momentum source term} [$/m^3$]}
\entry{$S_h$}{\hl{Energy source term} [$W/m^3$]}
\entry{$S_k$}{\hl{Species source term} [$kg/m^3$]}
\entry{$T_g$}{Gas temperature [$K$]}
\entry{$T_p$}{Particle temperature [$K$]}
\entry{$t$}{Time [$s$]}
\entry{$u$}{Velocity [$m/s$]}
\entry{$V$}{Volume [$m^3$]}
\entry{$Y_k$}{Species mass fraction [$kg/kg$]}
\entry{$x$}{Quality [$-$]}
\entry{}{\textit{Greek Variables}}
\entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
\entry{$\alpha_H$}{Mixture void fraction [$-$]}
\entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
\entry{$\epsilon_p$}{Particle emissivity [$-$]}
\entry{$\rho$}{Gas density [$kg/m^3$]}
\entry{$\rho_{eff}$}{Effective density [$kg/m^3$]}
\entry{$\rho_g$}{Gas density [$kg/m^3$]}
\entry{$\rho_l$}{Liquid density [$kg/m^3$]}
\entry{$\rho_M$}{Mixture density [$kg/m^3$]}
\entry{$\rho_p$}{Particle density [$kg/m^3$]}
\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant [$W/m^2K^4$]}
\entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
\entry{$\phi$}{Scalar variable [$-$]}
\entry{}{\textit{Abbreviations}}
\entry{$MCR$}{Maximum continuous rating}
\entry{$CFPP$}{Coal fired power plant}
\entry{$CFD$}{Computational fluid dynamics}
\entry{$SH$}{Superheater}
\entry{$EE$}{Eulerian-Eulerian}
\entry{$WSGGM$}{Weighted sum of gray gas model}
\entry{$RTE$}{Radiative transport equation}
\entry{$HHV$}{Higher heating value}
\entry{$DAF$}{Dry ash free}
\entry{$AR$}{As-received}
\entry{$PA$}{Primary air}
\entry{$SA-AH$}{Secondary air - air heater}
\entry{$SA$}{Secondary air}
\entry{$RH$}{Reheater}
\entry{$ATT$}{Attemperator}
\entry{$EC$}{Economiser}
\end{nomenclature}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).\\

Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}. The works of Belosevic et al \cite{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40\%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \cite{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions. The aforementioned research specifically investigated combustion and gas-side effects.\\

Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy. However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\
\newpage
The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\

@@

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. \hl{The governing equations for the gas phase are written below in their respective Reynolds averaged forms}.\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=\highlight{S}
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\\
&\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{split}
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows:
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

@@

A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
\newpage
The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabularx}{3.25in}{p{0.4in} p{1.25in} l}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabularx}
\end{table}
